### 2017-08-15 paper/codes/evaluation.tex
Adjusted vspace and deleted unnecessary comment in RQ1
pass on intro and evaluation (up to and including III.A)
Removed unnecessary comment
Uploading preliminar updates

\begin{figure}[h!]
\centering
\scriptsize
\lstset{
    escapeinside={@}{@},
    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
    basicstyle=\ttfamily\scriptsize, boxpos=c, numberstyle=\tiny,
    showstringspaces=false
}
\begin{lstlisting}[language=Bash]
MAVEN_IGNORES="-Dmaven.javadoc.skip=true -Drat.skip=true \
    -Djacoco.skip=true -Dcheckstyle.skip=true \
    -Dfindbugs=true -Dcobertura.skip=true"

for subj in $SUBJECTS; do
    cd $SUBJECTS_HOME/$subj
    mvn clean install -DskipTests $MAVEN_IGNORES
    mvn dependency:go-offline
    mvn -o test $MAVEN_IGNORES &> $LOG
    cat $LOG | grep "\[INFO\] Total time:"
done
\end{lstlisting}
\caption{\label{fig:mvn-execution} Bash script to evaluate the time cost of
    test suites. For each subject, we compile the source and test files, fetch
    all dependencies, and execute the tests in offline mode ignoring
    non-related tasks. Unnecessary commands are omitted for simplicity.}
\end{figure}

>>>>

\begin{figure}[h!]
\centering
\scriptsize
\lstset{
    escapeinside={@}{@},
    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
    basicstyle=\ttfamily\scriptsize, boxpos=c, numberstyle=\tiny,
    showstringspaces=false
}
\begin{lstlisting}[language=Bash]
MAVEN_SKIPS="-Drat.skip=true -Dmaven.javadoc.skip=true \
    -Djacoco.skip=true -Dcheckstyle.skip=true \
    -Dfindbugs.skip=true -Dcobertura.skip=true \
    -Dpmd.skip=true -Dcpd.skip=true"

for subj in $SUBJECTS; do
    cd $SUBJECTS_HOME/$subj
    mvn clean dependency:go-offline
    mvn test-compile install -DskipTests $MAVEN_SKIPS \
        &> compile.log
    mvn test -o -fae $MAVEN_SKIP &> testing.log
    cat testing.log \
        | grep --text "\[INFO\] Total time:" \
        | tail -n 1
done
\end{lstlisting}
\caption{\label{fig:mvn-execution} Bash script to measure time cost of
  test suites. For each subject, we fetch all dependencies,
  compile the source and test files, and execute the tests in
  offline mode ignoring non-related tasks. Test-unrelated tasks
  are omitted.}
\end{figure}

### 2017-08-15 paper/evaluation.tex
Uploading preliminar updates

We took the following actions to isolate our environment from
measurement noise.  First, we observed that some test tasks called
test-unrelated tasks (\eg, \emph{javadoc} generation and static
analyses) that could interfere in our time measurements.  To address
that potential issue, we inspected Maven execution logs from a sample
including a hundred projects prior to running the script from
Figure~\ref{fig:mvn-execution}.  The tasks we found were ignored from
execution (lines 1-3).  Furthermore, to avoid noise from operating
system events, we configured our workstation to run only essential
services.  The machine was dedicated to our experiments and we
accessed it via SSH. In addition, we configured the \CodeIn{isolcpus}
option from the Linux Kernel \cite{linux-kernel} to isolate six
virtual CPUs to run our experiments, leaving the remaining CPUs to run
OS processes~\cite{isolcpus-use}.  The rationale for this decision is
to prevent context-switching between user processes (running the
experiment) and OS-related processes.  Finally, to make sure our
measurements were fair, we compared timings corresponding to the
sequential execution of tests using Maven with that obtained with
JUnit's default \CodeIn{JUnitCore} runner, invoked from the command
line.  Results were very close.

The main loop (lines 5-11) of the script in
Figure~\ref{fig:mvn-execution} iterates over the list of subjects and
invokes Maven multiple times\Comment{ to isolate cost of running
  tests} (lines 7-9).  It first compiles the source and test files
(line 7), make all dependencies available locally (line 8), and then
runs the tests in offline mode as to skip the package update task,
enabled by default (line 9). After execution, we used a regular
expression on the output log to extract elapsed time (line 10).

%% We executed each project's test suite for
%% \Fix{5} times through Maven and directly through JUnit each project

@@

\begin{figure}[h]
    \centering
    \begin{subfigure}{0.47\textwidth}
      \centering
      \includegraphics[width=\textwidth]{plots/testcost-long.pdf}
      \caption{\label{fig:longtcost}Long group.}
    \end{subfigure}\\
    \vspace{2ex}
    \begin{subfigure}{0.47\textwidth}
      \centering
      \includegraphics[width=\textwidth]{plots/testcost-medium.pdf}
      \caption{\label{fig:medtcost}Medium group.}
    \end{subfigure}
    %% \vspace{2ex}
    %% \begin{subfigure}{0.5\textwidth}
    %%   \centering
    %%   \begin{tabular}{rrrr}
    %%     \toprule
    %%     & $\sigma\leq1$ & $1<\sigma\leq5$ & $\sigma\ge5$ \\
    %%     \midrule    
    %%     Long   &  7 & 15 & 12 \\
    %%     Medium & 22 & 19 & 7 \\
    %%     \bottomrule
    %%   \end{tabular}
    %%   \caption{\label{fig:sd}Standard deviation ($\sigma$) of test case running times.}
    %% \end{subfigure}
    \caption{\label{fig:time-distributions}Time distributions.}%
\end{figure}

>>>>

We took the following actions to isolate our environment from
measurement noise.  First, we observed that some test tasks called
test-unrelated tasks (\eg, \emph{javadoc} generation and static
analyses) that could interfere in our time measurements.  To address
that potential issue, we inspected Maven execution logs from a sample
including a hundred projects prior to running the script from
Figure~\ref{fig:mvn-execution}.  The tasks we found were ignored from
execution (lines 1-4).  Furthermore, to avoid noise from operating
system events, we configured our workstation to run only essential
services.  The machine was dedicated to our experiments and we
accessed it via SSH. In addition, we configured the \CodeIn{isolcpus}
option from the Linux Kernel \cite{linux-kernel} to isolate six
virtual CPUs to run our experiments, leaving the remaining CPUs to run
OS processes~\cite{isolcpus-use}.  The rationale for this decision is
to prevent context-switching between user processes (running the
experiment) and OS-related processes.  Finally, to make sure our
measurements were fair, we compared timings corresponding to the
sequential execution of tests using Maven with that obtained with
JUnit's default \CodeIn{JUnitCore} runner, invoked from the command
line.  Results were very close.
\Jbc{This is not true for projects running tests in parallel by defaut.
Recall from RQ3 that some projects run tests in parallel by default.
How should we address this?}

The main loop (lines 6-15) of the script in
Figure~\ref{fig:mvn-execution} iterates over the list of subjects and
invokes Maven multiple times\Comment{ to isolate cost of running
tests} (lines 8-11).  It first makes all dependencies available locally
(line 8), compiles the source and test files (line 9), and then runs
the tests in offline mode as to skip the package update task, enabled
by default (line 11). After execution, we used a regular expression on
the output log to extract the elapsed time (line 12-14).

@@

\begin{figure}[h]
    \centering
    \begin{subfigure}{0.47\textwidth}
      \centering
      \includegraphics[width=\textwidth]{plots/testcost-long.pdf}
      \caption{\label{fig:longtcost}Long group.}
    \end{subfigure}\\
    \vspace{2ex}
    \begin{subfigure}{0.47\textwidth}
      \centering
      \includegraphics[width=\textwidth]{plots/testcost-medium.pdf}
      \caption{\label{fig:medtcost}Medium group.}
    \end{subfigure}
    %% \vspace{2ex}
    %% \begin{subfigure}{0.5\textwidth}
    %%   \centering
    %%   \begin{tabular}{rrrr}
    %%     \toprule
    %%     & $\sigma\leq1$ & $1<\sigma\leq5$ & $\sigma\ge5$ \\
    %%     \midrule    
    %%     Long   &  7 & 15 & 12 \\
    %%     Medium & 22 & 19 & 7 \\
    %%     \bottomrule
    %%   \end{tabular}
    %%   \caption{\label{fig:sd}Standard deviation ($\sigma$) of test case running times.}
    %% \end{subfigure}
    \caption{\label{fig:time-distributions}Time distributions. X-axis
        denote projects appearing in arbitrary order.}%
\end{figure}

### 2017-08-15 paper/threats.tex
pass
Uploading preliminar updates

The main threats to validity of this study are the following.
\textit{External Validity:} Generalization of our findings is limited
to our selection of subjects, testing framework, and build system.  To
mitigate that issue, we selected subjects according to an objective
criteria, described in Section~\ref{sec:subjects}.  It remains to
evaluate the extent to which our observations would change when using
different testing frameworks and build systems.  \textit{Internal
  Validity:} Our results could be influenced by unintentional mistakes
made by humans who interpreted survey data and implemented scripts and
code to collect and analyze data. For example, we developed JUnit
runners to reproduce Maven's parallel configurations.  All those tasks
could introduce bias.  To mitigate those threats, we worked in pairs
as to increase chances of capturing unintentional mistakes.
\textit{Construct Validity:} We considered a number of metrics in this
study that could influence some of our interpretations.  For example,
we measured number of test cases per suite, distribution of test costs
in a suite, time to run a suite, etc.  In principle, these metrics may
not reflect the main problems associated with test
efficiency.\Mar{...elaborate...}

>>>>

The main threats to validity of this study are the following.
\textit{External Validity:} Generalization of our findings is limited
to our selection of subjects, testing framework, and build system.  To
mitigate that issue, we selected subjects according to an objective
criteria, described in Section~\ref{sec:subjects}.  It remains to
evaluate the extent to which our observations would change when using
different testing frameworks and build systems.  \textit{Internal
  Validity:} Our results could be influenced by unintentional mistakes
made by humans who interpreted survey data and implemented scripts and
code to collect and analyze data. For example, we developed JUnit
runners to reproduce Maven's parallel configurations and implemented
several scripts to automate our experiments.  All those tasks
could introduce bias in our results.  To mitigate those threats, we
worked in pairs as to increase chances of capturing unintentional
mistakes. Also, we re-executed our experiments on different machines
with different hardware to ensure that our results are consistent.
\textit{Construct Validity:} We considered a number of metrics in this
study that could influence some of our interpretations.  For example,
we measured number of test cases per suite, distribution of test costs
in a suite, time to run a suite, etc.  In principle, these metrics may
not reflect the main problems associated with test
efficiency.
 \Jbc{remember to mention failing tests and how we mitigate
this threat}
